---
title: "R Tutorial 1"
author: "Roseliz Ríos Alemar"
date: "2025-09-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assigning values

Q1. Create an object called height with the value 175. Print it. (Crea un objeto llamado height con el valor 175. Muéstralo en pantalla.)
```{r}
height <- 175
height
```
## Simple math

Q2. Calculate the result of 25 * 4 - 10. (Calcula el resultado de 25 * 4 - 10.)
```{r}
25*4 -10
```
## Using functions

Q3. Use the function sqrt() to calculate the square root of 81. (Usa la función sqrt() para calcular la raíz cuadrada de 81.)
```{r}
sqrt(81)
```
## Character objects

Q4. Assign the phrase “R is fun!” to an object called message. Print it. (Asigna la frase “R is fun!” a un objeto llamado message. Muéstralo.)
```{r}
message <- "R is fun!"
message
```
## Object manipulation

Q5. Create two objects a <- 10 and b <- 5. Calculate their sum and store it in c. (Crea dos objetos a <- 10 y b <- 5. Calcula su suma y guárdala en c.)
```{r}
a <- 10
b <- 5
a + b
c = a + b
c
```
## Logical comparison

Q6. Test whether 15 is greater than 20. (Verifica si 15 es mayor que 20.)
```{r}
15>20
```
## Checking classes

Q7. Check the class of the object "Hello World". (Verifica la clase del objeto "Hello World".)
```{r}
my_obj1 <- "Hello world"
my_obj1

class(my_obj1)
```
## Code chunk options

Q8. Run the following code chunk: <br>
- Observe the warnings that appear. (Observa las advertencias que aparecen.) <br>
- Modify the chunk options to suppress warnings without changing the code itself. (Modifica las opciones del chunk para apagar la advertencia sin cambiar el código.) <br>
```{r, warning=FALSE}
log(-1)
```
## Code chunk options

Q9. Run the following code chunk: <br>
- Observe the messages that appear. (Observa los mensajes que aparecen.) <br>
- Modify the chunk options to suppress messages without changing the code itself. (Modifica las opciones del chunk para apagar mensajes sin cambiar el código.)
```{r}
library(dplyr)
```
## Help files

Q10. Use R’s help system to find out what the function mean() does. (Usa el sistema de ayuda de R para averiguar qué hace la función mean())
```{r}
?mean()
```

